Acceleration of Derivative Calculations with Application to Radial Basis Function ­ Finite-Differences on the Intel MIC Architecture

### 2014-06-12 slides/2014_ics/slides-ics.tex
Modified a few plural errors, and replaced N by $N$ in a figure caption.

      \begin{itemize}
      \item Radial symmetry.
      \item RBFs approximate a function $f$ sampled at N distinct location $$f(\vec{r}) = \sum_i w_i \phi(||\vec{r}-\vec{r_i}||)$$ 
      \end{itemize}
    \end{block}

@@

      The DM has exactly $n$ non zero per row.
    \end{block}

@@

    In other words, the non zeros are at the same positions in the
    matrix, only the values of the non zero change.

    Benefits:
    \begin{itemize}
    \item Matrix compression: 1 column ID, 4 nonzero value. (gain: 38\%)
    \item Vector reusage.
    \end{itemize}
  \end{block}
\end{frame}

@@

    Number of floating point operation:\\$O = 2 n_v n_m n_c = 2 n_v n_m n_z n_r$
  \end{columns}

>>>>

      \begin{itemize}
      \item Radial symmetry.
      \item RBFs approximate a function $f$ sampled at $N$ distinct locations $$f(\vec{r}) = \sum_i w_i \phi(||\vec{r}-\vec{r_i}||)$$ 
      \end{itemize}
    \end{block}

@@

      The DM has exactly $n$ non-zeros per row.
    \end{block}

@@

    In other words, the non zeros are at the same positions in the
    matrix, only the non-zero values change.

    Benefits:
    \begin{itemize}
    \item Matrix compression: 1 column ID, 4 non-zero values. (gain: 38\%)
    \item Vector reusage.
    \end{itemize}
  \end{block}
\end{frame}

@@

    Number of floating point operations:\\$O = 2 n_v n_m n_c = 2 n_v n_m n_z n_r$
  \end{columns}
